resistanceModelNotesAndy

### 2015-05-22 resistanceModelNotesAndy.Rmd
notes

**20/5/15** 11- in liverpool meeting with Beth and train back

@@

@@

1. try to stop man pages being tracked by git, thy ar already in git ignore but I think I may need to do git delete or something delete them from the repo to stop git from tracking them
1. further develop sex-linkage in randomMating(), allow option to be passed as arg, plus may need to look at calculating genotypes of both m&f in runModel2()

>>>>

**20/5/15** 11-4 in liverpool meeting with Beth and train back

@@

**22/5/15**
To stop things being tracked by git that you have just added to gitignore
```
git rm --cached `git ls-files -i -X .gitignore` 
``` 
Then I just did commit from RStudio.

1. somehow I've broken the check
Failure(@testRefactoring.r#12): refactoring named variables with arrays doesn't change results 
runModel2(input, produce.plots = FALSE) not equal to runModel(input, produce.plots = FALSE)
Component "results": Component 1: 'is.NA' value mismatch: 186 in current 0 in target
Its because of Warning messages like this:
1: In runModel2(input) : Male frequencies before selection total != 1 0.997966163681722

Perhaps I need to make the checks less sensitive ??
Is it because I re-enabled checks that had been disabled by Beth ?
I reduced the tolerance in checks, runs OK, but tests still fail.

Points to some difference having crept in ...

difference is in 
genotype outputs in generations after 1
all those starting with RS1

to do with object genotype ....
Aha! problems were due to my new sex-linked changes that were operating without me realising.
So I should probaly remove the tolerances I put in. and work out how to reassign the impossible genotype freqs.

@@

1. check on implementation of sexLinkage in randomMating()

1. think I can remove genotype.freq it is the same as f['m',], I might want to create an fstart[] outside of the generations loop. This was prompted because previously genotype.freq was the same for males and females and it adds an unecessary extra layer of potential confusion

1. further develop sex-linkage in randomMating(), allow option to be passed as arg, plus may need to look at calculating genotypes of both m&f in runModel2()
